SOMETHING ABOUT THE DISTRIBUTED AVERAGING BASED APPROXIMATION IN SENSOR NETWORKS

### 2022-10-17 paper.tex

\begin{figure}[t]
    \centering
    \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
    \caption[]{}
    \label{fig:simulations:NPMtimedyn}
\end{figure}
\begin{figure}[t]
    \centering
    \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}
    \caption[]{}
    \label{fig:simulations:normtime}
\end{figure}
\begin{figure}[t]
    \centering
    \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}
    \caption[]{}
    \label{fig:simulations:normstime}
\end{figure}

>>>>

% \begin{figure}[t]
%     \centering
%     \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
%     \caption[]{}
%     \label{fig:simulations:NPMtimedyn}
% \end{figure}
% \begin{figure}[t]
%     \centering
%     \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}
%     \caption[]{}
%     \label{fig:simulations:normtime}
% \end{figure}
% \begin{figure}[t]
%     \centering
%     \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}
%     \caption[]{}
%     \label{fig:simulations:normstime}
% \end{figure}

\begin{figure}[t]
    \centering
    \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}\\\vspace*{-1.0cm}
    \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}\\\vspace*{-1.0cm}
    \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
    \caption[]{}
    \label{fig:simulations:NPMtimedyn}
\end{figure}
